Model LF

### 2022-10-03 max_dp endogen stød.Rmd
Commit changes
commit

plot(max_dp_00, col= "red"); lines(obs_dp_q, col = "blue"); 
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(komp_r_00, col= "red"); lines(komp_r_obs, col = "blue"); 
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

>>>>

plot(max_dp_00, col= "red"); lines(obs_dp_q, col = "blue"); 
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()

plot(komp_r_00, col= "red"); lines(komp_r_obs1, col = "blue"); 
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()
